---
title: "Timing in CHILDES"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(childesr)
library(DT)
```

If we could get a list of common overregularizations, we could:

- find all of the instances in CHILDES.

- We could figure out which corpora have audio or video, and we could hand-code the response onset for these irregulars. 

Which corpora have timestamped audio/video? We want to restrict this down to a smaller age range presumably
```{r}
utterances <- get_utterances(collection = c("Eng-NA", "Eng-UK"))

media_transcripts <- utterances %>%
  filter(!is.na(media_start)) %>%
  distinct(collection_id, corpus_id, corpus_name, transcript_id)

datatable(media_transcripts)

unique(media_transcripts$corpus_name)
```

Pick one kid for error timing coding
```{r}
thomas_corpus <- utterances %>%
  filter(corpus_name == "Thomas")

thomas_verbs <- thomas_corpus %>%
  mutate(has_verb = str_detect(part_of_speech, "v")) %>%
  group_by(transcript_id) %>%
  mutate(mom_response = (speaker_role == "Mother" & lag(speaker_role) == "Target_Child"),
         lag_verb = lag(has_verb),
         response_time = media_start - lag(media_end))

mom_responses <- thomas_verbs %>%
  filter(mom_response, lag_verb) %>%
  filter(response_time <= 3 & response_time >= -3) %>%
  mutate(age_floored = floor(target_child_age))


ggplot(mom_responses, aes(x = age_floored, y = response_time, group = age_floored)) + 
  geom_boxplot()
```

```{r}
fraser_corpus <- utterances %>%
  filter(target_child_name == "Fraser")


downstairs <- fraser_corpus %>%
  filter(str_detect(gloss, "downstairs"), speaker_code == "CHI")

fraser_errors <- fraser_corpus %>%
  mutate(error = str_detect(gloss, "\\*"),)
```


- We could construct some comparison set of utterances, either a random sample from the same parent/child dyads, or we could try to control for things about the overregularized items (e.g. we could compare to the correct regular form). Or another past-tense verb that it similar somehow. 

```{r load-kids}
tokens <- get_tokens(collection = "Eng-NA", token = "runned")

utterances <- get_utterances(corpus = "NewEngland")
```


Promising corpora: Nelson, Sachs, Snow, Wiest, Braunwald, Forrester, Tommerdahl
Maybe: Providence, MacWhinney, Bloom


Individual Corpus Information

Nelson
Goes up to 2 years 8 mo, errors marked but fixed in database
```{r}
Nelson_corpus <- utterances %>%
  filter(corpus_name == "Nelson")
```

Providence
Cannot find on the website? But seems to go up to 3 years, 6 children
```{r}
prov_corpus <- utterances %>%
  filter(corpus_name == "Providence")
unique(prov_corpus$target_child_name)
```

MacWhinney
Up to 7 years, not sure if all the transcripts on the website load into data base because I couldn't find an error example I'd found for "Ernie want hot dog"
```{r}
MW_corpus <- utterances %>%
  filter(corpus_name == "MacWhinney")
```

Sachs
up to 4 years
looks like they mark error, found an example of plural error in 030400
AND Database doesn't edit it
```{r}
Sachs_corpus <- utterances %>%
  filter(corpus_name == "Sachs")
```

Snow
goes up to age three, looks like a lot of book reading together (don't know if that changes things), can't find error examples
```{r}
Snow_corpus <- utterances %>%
  filter(corpus_name == "Snow")
```

Weist
6 kids, ages 2-4, looks like errors are marked but not in database
```{r}
Weist_corpus <- utterances %>%
  filter(corpus_name == "Weist")
```

Braunwald
age 1-4, errors are marked, looks like they're not corrected 
example: 030311, "I go bigger"
```{r}
Braunwald_corpus <- utterances %>%
  filter(corpus_name == "Braunwald")
```

Bloom70
Peter is the only one with media, up to 3 years (but most at around 2 or less), don't know if all the media markings are loading in the database
```{r}
Bloom_corpus <- utterances %>%
  filter(corpus_name == "Bloom70")
```

Forrester
videos age 1-3, can't find error information
```{r}
Forrester_corpus <- utterances %>%
  filter(corpus_name == "Forrester")
```

Tommerdahl
age looks like 30mo-50mo, but they don't indicate which child is which
I did find an error marking in LP2 for "broked", and they did not correct in database
```{r}
Tommerdahl_corpus <- utterances %>%
  filter(corpus_name == "Tommerdahl")
```

-------------------------------------------------------------------------------------

McMillan
short, 3 10-minute videos, one of each kid individually and then all three together
```{r}
mm_corpus <- utterances %>%
  filter(corpus_name == "McMillan")
```

Brent
collection of kids around a year old
```{r}
Brent_corpus <- utterances %>%
  filter(corpus_name == "Brent")
```

Peters
up to 2 years, hard for me to find examples of errors
```{r}
Peters_corpus <- utterances %>%
  filter(corpus_name == "Peters")

```

Sawyer
Whole group of kids & parents together at once
```{r}
Sawyer_corpus <- utterances %>%
  filter(corpus_name == "Sawyer")
```

McCune
collection of kid videos, not all transcribed, most in the first year and then one at year 2

VanHouten
29 different kids, looks like short interactions
```{r}
VH_corpus <- utterances %>%
  filter(corpus_name == "VanHouten")
unique(VH_corpus$target_child_name)
```

Bernstein
Very young <2
```{r}
Bernstein_corpus <- utterances %>%
  filter(corpus_name == "Bernstein")
```

Gleason
3 recordings of each child, 24 children, ages 3-4, one as a group at dinner and I think the other two as separate times with each parent
```{r}
Gleason_corpus <- utterances %>%
  filter(corpus_name == "Gleason")
unique(Gleason_corpus$target_child_name)
```

Rollins
A year old or less
```{r}
Rollins_corpus <- utterances %>%
  filter(corpus_name == "Rollins")
```

Soderstorm
6mo to a year
```{r}
Sod_corpus <- utterances %>%
  filter(corpus_name == "Soderstorm")
```
