---
title: "Timing in CHILDES"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(childesr)
library(DT)
```

If we could get a list of common overregularizations, we could:

- find all of the instances in CHILDES.

- We could figure out which corpora have audio or video, and we could hand-code the reponse onset for these irregulars. 

Which corpora have timestamped audio/video? We want to restrict this down to a smaller age range presumably
```{r}
utterances <- get_utterances(collection = c("Eng-NA", "Eng-UK"))

media_transcripts <- utterances %>%
  filter(!is.na(media_start)) %>%
  distinct(collection_id, corpus_id, corpus_name, transcript_id)

datatable(media_transcripts)
```

- We could construct some comparison set of utterances, either a random sample from the same parent/child dyads, or we could try to control for things about the overregularized items (e.g. we could compare to the correct regular form). Or another past-tense verb that it similar somehow. 

```{r load-kids}
tokens <- get_tokens(collection = "Eng-NA", token = "runned")

utterances <- get_utterances(corpus = "NewEngland")
```
